### 2018-05-10 vipassana-for-hackers.tex
Apply fixes by @sycrat and @liammonahan in the base repo
Co-authored-by: Aaron Blair <aaron@aaronpb.me>
Co-authored-by: Liam Monahan <liam@liammonahan.com>
typo fix

The first 3.5 days of a 10-day Vipassana course are spend practicing ``Anapana'' (breath) meditation. This period is very important as it is time spent practicing acute, one-pointed attention. If we visualize our attention as any skin (internal or external; lips, nose, nostrils, etc.) covered by the pink triangle in Figure~\ref{fig:burmese-anapana-triangle}, we will get an idea of exactly where one's attention is directed at the beginning of Anapana practice.

@@

What is meant by ``prodding our nervous system'' and what does this have to do with brain activity? Our second suspension of disbelief was of the deep and intense connection between the brain the nervous system. We cannot feel the brain directly --- or at all. Thanks to the deep interconnection between the brain and the nervous system, however, the body acts as a surface to which we have ready access --- and which in turn provides us access to the brain. This brain/body connection can be thought of as \textit{mutual recursion}, as the term is used in the previous section.

>>>>

The first 3.5 days of a 10-day Vipassana course are spent practicing ``Anapana'' (breath) meditation. This period is very important as it is time spent practicing acute, one-pointed attention. If we visualize our attention as any skin (internal or external; lips, nose, nostrils, etc.) covered by the pink triangle in Figure~\ref{fig:burmese-anapana-triangle}, we will get an idea of exactly where one's attention is directed at the beginning of Anapana practice.

@@

What is meant by ``prodding our nervous system'' and what does this have to do with brain activity? Our second suspension of disbelief was of the deep and intense connection between the brain and the nervous system. We cannot feel the brain directly --- or at all. Thanks to the deep interconnection between the brain and the nervous system, however, the body acts as a surface to which we have ready access --- and which in turn provides us access to the brain. This brain/body connection can be thought of as \textit{mutual recursion}, as the term is used in the previous section.
